---
title: "Barcorde Based Student Record System"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    social: [ "twitter", "facebook", "menu"]
    source_code: embed
---


```{r setup, include=FALSE}
library(flexdashboard)
library(knitr)
library(DT)
library(ggplot2)
library(rpivotTable)
library(plotly)
library(dplyr)
library(highcharter)
library(openintro)
library(scales)
```
```{r}
roi<-read.csv("roi.csv")
nps<-read.csv("nps.csv")
survey<-read.csv("surveys.csv")
Si<-read.csv("system_incidents.csv")
nf<-read.csv("new_features.csv")
ip<-read.csv("investment_proposals.csv")
et<-read.csv("employee_training.csv")
av<-read.csv("Average_response_time.csv")
```
```{r}
mycolors<-c("grey","blue","maroon","#D4AF37")
```

Internal Business Processes Perspective
===========================================
Row
---------------------------------------
### Total Number of Trainings
```{r}
valueBox(sum(et$Employee.Training),
         icon = "fa-bicycle")
```

### Total Number of New features
```{r}
valueBox(sum(nf$New.Features),
         icon = "fa-bicycle")
```

### Trainings Per New Feature
```{r}
Traingings_per_new_feature=sum(et$Employee.Training)/sum(nf$New.Features)
gauge(round(Traingings_per_new_feature,
            digits = 2),
            min = 0,
            max = 3,
            gaugeSectors(success = c(2, 3),
                         warning = c(0.5,1 ),
                         danger = c(0, 0.5),
                         colors = c("green", "yellow", "red")))
```

Row
---------------------------------------

```{r}
p2 <- et %>%
         group_by(et$Year.2020) %>%
         summarise(et$Employee.Training) %>%
         plot_ly(labels = ~et$Year.2020,
                 values = ~et$Employee.Training,
                 marker = list(colors = mycolors)) %>%
         add_pie(hole = 0.5) %>%
         layout(xaxis = list(zeroline = F,
                             showline = F,
                             showticklabels = F,
                             showgrid = F),
                yaxis = list(zeroline = F,
                             showline = F,
                             showticklabels=F,
                            showgrid=F))
p2 
```

### Employees' Trainings 

```{r}
p1 <- nf %>%
         group_by(nf$Year) %>%
         summarise(sum(nf$New.Features)) %>%
         plot_ly(x = ~nf$Year,
                 y = ~nf$New.Features,
                 type = 'bar',
                 marker = list(color = 'blue')) %>%
         layout(xaxis = list(title = "Year"),
                yaxis = list(title = 'Number of Trainings'))
p1
```

### 
```{r}
p1 <- et %>%
         group_by(et$Year.2020) %>%
         summarise(sum(et$Employee.Training)) %>%
         plot_ly(x = ~et$Employee.Training,
                 y = ~et$Year.2020,
                 type = 'bar',
                 marker = list(color = 'blue')) %>%
         layout(xaxis = list(title = "Year"),
                yaxis = list(title = 'Number of Trainings'))
p1
```

Innovation and Learning Perspective
===========================================
Row 
--------------------------------------
### Total time taken
```{r}
valueBox(sum(av$Time.taken.to.respond..sec.),
         icon = "fa-bicycle")
```

### Average Response Time 

```{r}
gauge(round(5.5,
            digits = 2),
            min = 0,
            max = 10,
            gaugeSectors(success = c(7, 10),
                         warning = c(5.,8 ),
                         danger = c(0, 4),
                         colors = c("green", "yellow", "red")))
```

### Mode of the Response Time

```{r}
gauge(round(12,
            digits = 2),
            min = 0,
            max = 10,
            gaugeSectors(success = c(12, 15),
                         warning = c(8,11 ),
                         danger = c(0, 7),
                         colors = c("green", "yellow", "red")))
```

###Total Time taken

```{r}

```


Row 
--------------------------------------
### System Incidents 
```{r}
p3 <- Si %>%
 group_by(Si$Year.2022) %>%
         summarise(sum(Si$System.uptime.incidents)) %>%
         plot_ly(x = ~Si$Year.2022,
                 y = ~Si$System.uptime.incidents,
                 type = 'bar',
                 marker = list(color = '#D4AF37')) %>%
         layout(xaxis = list(title = "2022"),
                yaxis = list(title = 'Number of system uptime incidents'))
p3
```


Customer's Perspective
===========================================
Row
------------------------------------------------------
### Average NPS 
```{r}
gauge(round(mean(nps$Net.Promoter),
            digits = 2),
            min = -100,
            max = 100,
            gaugeSectors(success = c(50, 100),
                         warning = c(0,50 ),
                         danger = c(-100, 0),
                         colors = c("green", "yellow", "red")))
```

### 2019 NPS 
```{r}
gauge(round(85,
            digits = 2),
            min = -100,
            max = 100,
            gaugeSectors(success = c(60, 100),
                         warning = c(0,60 ),
                         danger = c(-100, 0),
                         colors = c("green", "yellow", "red")))
```

### 2020 NPS 
```{r}
gauge(round(60,
            digits = 2),
            min = -100,
            max = 100,
            gaugeSectors(success = c(70, 100),
                         warning = c(0,70 ),
                         danger = c(-100, 0),
                         colors = c("green", "yellow", "red")))
```
### 2021 NPS 
```{r}
gauge(round(75,
            digits = 2),
            min = -100,
            max = 100,
            gaugeSectors(success = c(60, 100),
                         warning = c(0,60 ),
                         danger = c(-100, 0),
                         colors = c("green", "yellow", "red")))
```
### 2022 NPS 
```{r}
gauge(round(89,
            digits = 2),
            min = -100,
            max = 100,
            gaugeSectors(success = c(60, 100),
                         warning = c(0,60 ),
                         danger = c(-100, 0),
                         colors = c("green", "yellow", "red")))
```
Row
--------------------------------------------------
### NPS by Year
```{r}
p3 <- nps %>%
 group_by(nps$Year) %>%
         summarise(sum(nps$Net.Promoter)) %>%
         plot_ly(x = ~nps$Year,
                 y = ~nps$Net.Promoter,
                 type = 'bar',
                 marker = list(color = '#D4AF37')) %>%
         layout(xaxis = list(title = "2022"),
                yaxis = list(title = 'Net promoter Score'))
p3
```
### Number of Surveys 
```{r}
p3 <- survey %>%
 group_by(survey$Year) %>%
         summarise(sum(survey$Student.Surveys)) %>%
         plot_ly(x = ~survey$Year,
                 y = ~survey$Student.Surveys,
                 type = 'bar',
                 marker = list(color = 'blue')) %>%
         layout(xaxis = list(title = "2022"),
                yaxis = list(title = 'Number of Survey '))
p3
```

Financial Perspective
===========================================
Row
----------------------------------------------
### Total Investment Aount
```{r}
MillionForm <- dollar_format(prefix = "$",suffix="M")
valueBox(MillionForm((sum(ip$Investment.Amount..million.))),
        icon = "fa-money",
        color='white')
```
### Total Approved Investment Amount
```{r}
MillionForm <- dollar_format(prefix = "$",suffix="M")
valueBox(MillionForm(25),
        icon = "fa-money",
        color='white')
```
### Average Expected  Roi
```{r}
gauge((scales::percent(mean(ip$Expected.ROI....)/100)),
            min = 0,
            max = 50,
            gaugeSectors(success = c(25, 50),
                         warning = c(24, 15),
                         danger = c(0, 14),
                         colors = c("green", "darkorange", "red")))
```
Row
-----------------------------------------------
### Total Invesment Amount by Proposal Type
```{r}
p4 <- ip %>%
  filter(!is.na(ip$Proposal.Name)) %>%
  group_by(ip$Proposal.Name) %>%
  plot_ly(labels = ~ip$Proposal.Name,
          values = ~ip$Investment.Amount..million.,
          marker = list(colors = mycolors)) %>%
  add_pie(hole = 0.5) %>%
  layout(xaxis = list(zeroline = F,
                      showline = F,
                      showticklabels = F,
                      showgrid = F),
         yaxis = list(zeroline = F,
                      showline = F,
                      showticklabels = F,
                      showgrid = F))
p4

```

### Total Invesment Amount by Year
```{r}
p3 <- ip %>%
 group_by(ip$Year) %>%
         summarise(sum(ip$Investment.Amount..million.)) %>%
         plot_ly(x = ~ip$Year,
                 y = ~ip$Investment.Amount..million.,
                 type = 'bar',
                 marker = list(color = 'blue')) %>%
         layout(xaxis = list(title = "Year"),
                yaxis = list(title = 'Investment Amount '))
p3
```
### Investment Amount by Status
```{r}
p4 <- ip %>%
  filter(!is.na(ip$Proposed.Status)) %>%
  group_by(ip$Proposed.Status) %>%
  plot_ly(labels = ~ip$Proposed.Status,
          values = ~ip$Investment.Amount..million.,
          marker = list(colors = mycolors)) %>%
  add_pie(hole = 0.5) %>%
  layout(xaxis = list(zeroline = F,
                      showline = F,
                      showticklabels = F,
                      showgrid = F),
         yaxis = list(zeroline = F,
                      showline = F,
                      showticklabels = F,
                      showgrid = F))
p4

```
Row
-----------------------------------------------
### Expected ROI by Proposal Type
```{r}
p4 <- ip %>%
  filter(!is.na(ip$Proposal.Name)) %>%
  group_by(ip$Proposal.Name) %>%
  plot_ly(labels = ~ip$Proposal.Name,
          values = ~ip$Expected.ROI....,
          marker = list(colors = mycolors)) %>%
  add_pie(hole = 0.5) %>%
  layout(xaxis = list(zeroline = F,
                      showline = F,
                      showticklabels = F,
                      showgrid = F),
         yaxis = list(zeroline = F,
                      showline = F,
                      showticklabels = F,
                      showgrid = F))
p4

```

### Expected ROI by Year
```{r}
p3 <- ip %>%
 group_by(ip$Year) %>%
         summarise(sum(ip$Expected.ROI....)) %>%
         plot_ly(x = ~ip$Year,
                 y = ~ip$Expected.ROI....,
                 type = 'bar',
                 marker = list(color = 'blue')) %>%
         layout(xaxis = list(title = "Year"),
                yaxis = list(title = 'Expected ROI in % '))
p3
```
### Expected ROI by Status
```{r}
p4 <- ip %>%
  filter(!is.na(ip$Proposed.Status)) %>%
  group_by(ip$Proposed.Status) %>%
  plot_ly(labels = ~ip$Proposed.Status,
          values = ~ip$Expected.ROI....,
          marker = list(colors = mycolors)) %>%
  add_pie(hole = 0.5) %>%
  layout(xaxis = list(zeroline = F,
                      showline = F,
                      showticklabels = F,
                      showgrid = F),
         yaxis = list(zeroline = F,
                      showline = F,
                      showticklabels = F,
                      showgrid = F))
p4

```

# International business occurs in many different formats: The movement of goods from country to another (exporting, importing, trade) Contractual agreements that allow foreign firms to use products, services, and processes from other nations (licensing, franchising)